flowCore: data structures package for flow cytometry data

### 2007-04-16 inst/doc/HowTo-flowCore.Rnw
vignette
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@23923 bc3139a8-67e5-0310-9ffc-ced21a209358

<<Transfo2, fig=true, prefix=FALSE, include=FALSE, echo=true>>=
plot(transform(fs[[1]], log.FL1.H=log(`FL1-H`), log.FL2.H=log(`FL2-H`)), c("log.FL1.H", "log.FL2.H"))
@

\begin{figure}
\centering
\includegraphic{Transfo2}
\end{figure}

>>>>

<<Transfo2, fig=true, prefix=FALSE>>=
plot(transform(fs[[1]], log.FL1.H=log(`FL1-H`), log.FL2.H=log(`FL2-H`)), c("log.FL1.H", "log.FL2.H"))
@
